Cross Validation Analysis

### 2023-04-28 minos/validation/cross_validation.Rmd
Started R script for testing equivalent income
Changed names of a few functions

```{r, include=FALSE}
source('Minos/minos/validation/utils.r')
```

@@

```{r, include=FALSE}
# cross validation simulation output
out.path <- 'Minos/output/cross_validation/'
cv <- read_output(out.path, 'baseline')

>>>>

```{r, include=FALSE}
source('Minos/minos/utils_datain.R')
source('Minos/minos/validation/utils.r')
```

@@

```{r, include=FALSE}
# cross validation simulation output
out.path <- 'Minos/output/cross_validation/'
cv <- read_singular_local_out(out.path, 'baseline')
